---
title: "Lab #6 GES687 Laura Bayona-Roman"
output: 
        html_notebook:
                keep_md: true
date: April 12, 2021

---

### The purpose of this lab is to make a choropleth map with two variables. 

### Package Installation

```{r}
library (tidyverse)
library (tidycensus)
library(ggplot2)
library (sf)
```

### Running tigris and the census api key

```{r}
options(tigris_class="sf")
options(tigris_use_cache=TRUE)
census_api_key("94e4f22691ce947e64eb28fd8e9c0ba431c4b343", overwrite=TRUE)
```

### Importing census data-American Community Survey 2010 span of 3 years
### Percent of Puerto Ricans-Florida
```{r}
PR2010per<- get_acs(geography = "county", 
     variables ="DP05_0068PE",  
     year = 2010,
     survey = "acs3",
     state = c(12), 
     geometry = FALSE, 
     output = "wide") 
```

### Importing census data-American Community Survey 2013 span of 3 years
### Percent of Puerto Ricans-Florida
```{r}
PR2013per<- get_acs(geography = "county", 
     variables ="DP05_0068PE",  
     year = 2013,
     survey = "acs3",
     state = c(12), 
     geometry = TRUE, 
     output = "wide")
```

### Importing census data-American Community Survey 2010 span of 3 years
### Percent-Housing Occupancy-Vacant Housing Units
```{r}
HVacant2010per<- get_acs(geography = "county", 
     variables ="DP04_0003PE",  
     year = 2010,
     survey = "acs3",
     state = c(12), 
     geometry = FALSE, 
     output = "wide")
```

### Importing census data-American Community Survey 2013 span of 3 years
### Percent-Housing Occupancy-Vacant Housing Units
```{r}
HVacant2013per<- get_acs(geography = "county", 
     variables ="DP04_0003PE",  
     year = 2013,
     survey = "acs3",
     state = c(12), 
     geometry = TRUE, 
     output = "wide")
     
### Attempt to Plot Percent of Puerto Ricans 2013
```{r}
ggplot(PR2013per) + geom_sf(aes(fill = DP05_0068PE))
```
### Attempt to transform files- Puerto Ricans
```{r}
st_write(st_transform(PR2013per,3857), "PR2013per.geojson")
```
```{r}
st_write(PR2010per, "PR2010per.csv") 
```

### Attempt to transform files- Housing Vacancies
```{r}
st_write(st_transform(HVacant2013per,3857), "HVacant2013per.geojson")
```
```{r}
st_write(HVacant2010per, "HVacant2010per.csv") 
```

### Attempt at Merging Time Periods-Puerto Ricans 
```{r}
PR_Florida_per <- left_join(PR2013per, PR2010per,
                        by = "GEOID",
                        copy = FALSE,
                        suffix=c(".13",".10"))
```

### Attempt at Merging Time Periods- Housing Vacancies
```{r}
HVacant_Florida_per <- left_join (HVacant2013per,  HVacant2010per,
                              by = "GEOID",
                              copy = FALSE,
                              suffix = c(".13", ".10"))
```

### Attempt at Exporting To QGIS
```{r}
st_write(PR_Florida_per, "PR_Florida_per.geojson")
```
```{r}
st_write(HVacant_Florida_per, "HVacant_Florida_per.geojson")
```
